Project Review Template

### 2025-04-24 code/analysis-code/statistical-analysis.qmd
updated readme files

# 7. Save to file
ggsave(
  "/Users/alexisgonzalez/Desktop/MADA/Gonzalez-MADA-project/results/figures/seasonalpreds.png", 
  plot = seasonalpreds, width = 8, height = 6

@@

```{r}
library(mgcv)
gam_model <- gam(clinical_count ~ s(day_of_year), family = poisson(), data = daily_counts)
plot(gam_model)
ggsave("/Users/alexisgonzalez/Desktop/MADA/Gonzalez-MADA-project/results/figures/gam_model.png", plot = gam_model, width = 8, height = 6, dpi = 300)
```

>>>>

# 7. Save to file
ggsave(
  "/Users/alexisgonzalez/Desktop/MADA/Gonzalez-MADA-project/results/figures/seasonalpreds.png", 
  plot = seasonalpreds, width = 8, height = 6)

@@

```{r}
library(mgcv)
gam_model <- gam(clinical_count ~ s(day_of_year), family = poisson(), data = daily_counts)
plot(gam_model)
```
